---
title: "RegressionProject"
author: "Sebastián ZL"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
cat("\014") 
library(datasets)
data(mtcars)
```
# Executive summary 

This project aims to explore some features that affect fuel consumption in miles per gallon (MPG)  based on a  collection of cars (mtcars -  Motor Trend Car Road Tests) data set. This because Motor Trend Magazine is interested in exploring the relationship between a set of variables and miles per gallon (MPG). They are particularly interested in the following two questions:
- Is an automatic or manual transmission better for MPG?
- Quantifying how different is the MPG between automatic and manual transmissions?

## Exploratory data analysis 

```{r Resumen y graficos, echo=FALSE}
str(mtcars) #Resumen

mtcars$am.label <- factor(mtcars$am, labels=c("Automatic","Manual")) # 0=automatico, 1=manual Añade un label a la entrada variable de interés.

boxplot(mpg~am.label, data=mtcars, col="grey", ylab="Miles per gallon", xlab = "Transmission type", main="Miles per gallon by transmission type")
```

We proceed to see if theres a significant difference between average miles per galon beetwen the transmission type. 
````{r t-Test, echo=FALSE}
manu<-subset(mtcars,mtcars$am==1)
auto<-subset(mtcars,mtcars$am==0)
test<-t.test(auto$mpg,manu$mpg)
```
As we saw above, for a conventional significance level $\alpha=0.05$ under the null hypothesis of true diffence in means equal to zero, we \textbf{reject} this hypothesis with a p-value of 0.0014. This is also confirmed by the 95% confidence interval of  the means difference [-11.28,-3.20], which is not cointaining zero or near zero values. Now whe can proceed to calculate how different are the autonmyes.
```{r Linear regression, echo=FALSE}
fit<-lm(mtcars$mpg~as.factor(mtcars$am))
summary(fit)
```

The regression coefficient  \textit{"as.factor(mtcars\$am)1"} tell us that \textvf{manual cars have an 7.245mpg average above the automatica ones.} *** indicates that its p-value its contaiden in \textit{(0,001]} and its a statistically significant predictor. Unfurnately, as $R^2=03598$, only the 36% of the mpg variance its explained by the univariate model.