---
title: "RegressionProject"
author: "Sebastián ZL"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
cat("\014") 
library(datasets)
data(mtcars)
```
# Executive summary 

This project aims to explore some features that affect fuel consumption in miles per gallon (MPG)  based on a  collection of cars (mtcars -  Motor Trend Car Road Tests) data set. In particularly we want answer two questions:
- Is an automatic or manual transmission better for MPG?
- Quantifying how different is the MPG between automatic and manual transmissions?
## Exploratory data analysis 


```{r Resumen y graficos, echo=FALSE}
str(mtcars) #Resumen

mtcars$am.label <- factor(mtcars$am, labels=c("Automatic","Manual")) # 0=automatico, 1=manual Añade un label a la entrada variable de interés.

boxplot(mpg~am.label, data=mtcars, col="grey", ylab="Miles per gallon", xlab = "Transmission type", main="Miles per gallon by transmission type")
````
We proceed to see if theres a significant difference between average miles per galon beetwen the transmission type. 
````{r t-Test, echo=FALSE}
https://rpubs.com/RichFlorez/228366
```